---
title: "README"
author: "Zachary McCaw"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: TRUE
--- 

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE, 
  cache = FALSE
)
```

Zachary McCaw <br>
Updated: 2020-10-18

## Overview

Given stratified event-count data for two arms, this package calculates the marginal odds ratio of [Tian et al. (2009)](https://doi.org/10.1093/biostatistics/kxn034), and constructs the asymptotic and bootstrap confidence intervals. In contrast to the Mantel-Haenszel approach for combining odds ratios across strata, the present approach is to first calculate the marginal events in each arm by taking a stratum-size weighted average of the per-stratum event rates, then form the odds ratio. 

## Installation

```{r, eval=FALSE}
devtools::install_github(repo = 'zrmacc/MargOR')
```

## Example

Consider the following 28-day unadjusted mortality data from a recent [COVID-19 clinical trial](https://www.nejm.org/doi/full/10.1056/NEJMoa2021436), stratified by respiratory support at ranomization. The marginal odds ratio, comparing dexamethasone with usual care, is 0.861. 

```{r}

# Event counts.
y0 <- c(283, 682, 145)
n0 <- c(683, 2604, 1034)
y1 <- c(95, 298, 89)
n1 <- c(324, 1279, 501)

# Marginal Odds Ratio
library(MargOR)
or_analysis <- MargOR(
  y0 = y0,
  n0 = n0,
  y1 = y1,
  n1 = n1,
  alpha = 0.05,
  reps = 2e3
)
show(or_analysis)

```

The results of a Mantel-Haenszel test are similar:

```{r}
library(abind)
# Formatting data.
z0 <- n0 - y0
z1 <- n1 - y1

ctrl <- rbind(z0, y0)
trt <- rbind(z1, y1)

data <- abind(ctrl, trt, along = 0)
mantelhaen.test(data)

```


